---
title: "R Notebook"
output: 
  html_notebook: 
    theme: readable
    toc: yes
---

## Loading Packages & Data

Loading packages
```{r, results='hide'}
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

packages <- c("tidyverse", "ggpmisc", "broom", "gridExtra", "ggExtra")
ipak(packages)
```


Load in the data for the exercise
```{r, echo=TRUE}
ex8_data <- read.csv("/Users/Julian/GDrive/Misc/Classes/InterStats/Ex8_LabData.csv") %>% tbl_df()
```

<br />
Add a light theme for ggplot output.
```{r}
old <- theme_set(theme_light(base_size = 12))
```

## Scatterplot

Create a scatterplot with CESD scores at Time 1 and Time 2. 
```{r Test, echo=TRUE}
ggplot(ex8_data, aes(CESD1, CESD2)) + 
  geom_point()

```

<br />
Add a LOESS line (i.e., a smoothed or running average).
```{r}
ggplot(ex8_data, aes(CESD1, CESD2)) + 
  geom_point() + 
  geom_smooth()

```

## Correlation

Test the correlation between CESD1 and CESD2. 
```{r}
cor.test(ex8_data$CESD1, ex8_data$CESD2)

```

### BONUS: Boostrapped Confidence Interval
```{r}
set.seed(10302016)
nSims <- 1000
ex8_data %>% 
  bootstrap(nSims) %>% 
  do(tidy(cor(.$CESD1, .$CESD2))) %>% 
  ungroup() %>% select(pearson_r = x) %>% 
  arrange(pearson_r) %>% 
  slice( c(nSims*.025, nSims*.975)) %>% 
  mutate_all(funs(round(.,4))) %>% 
  add_column(bound = c("lower", "upper"))

```

## Regression

Test the linear regression of CESD time 1 scores predicting CESD at time 2.    
```{r}
m1 <- lm(CESD2 ~ CESD1, data=ex8_data)
summary(m1)
```

<br />
Use broom::tidy to output model summary into dataframe 
```{r}
tidy(m1)
glance(m1)
```

<br />
General equation for line of best fit:
$$
y = a + bx
$$
<br />
Plug in estimates to generate equation for line of best fit
$$
\hat{Y} = 2.57 + 0.45x
$$

<br />
Examine confidence interval of the estimates
```{r}
confint(m1)
```

<br />
Add linear regression fit onto scatterplot
```{r}
ggplot(ex8_data, aes(CESD1, CESD2)) + 
  geom_point() + 
  geom_smooth(method=lm)

```

<br />
Remember to add title and axes to your plots
```{r}

ggplot(ex8_data, aes(CESD1, CESD2)) + 
  geom_point() + 
  geom_smooth(method=lm) + 
  xlab("CESD at Time 1") + 
  ylab("CESD at Time 2") + 
  ggtitle("CESD at Time 2 as a function of CESD at Time 1")

```

### BONUS: Adding Equation
We can also add some code to superimpose the regression equation
```{r}

ggplot(ex8_data, aes(CESD1, CESD2)) + 
  geom_point() + 
  geom_smooth(method=lm) +
  xlab("CESD at Time 1") + 
  ylab("CESD at Time 2") + 
  ggtitle("CESD at Time 2 as a function of CESD at Time 1") +
  stat_poly_eq(aes(label =  paste(..eq.label.., ..adj.rr.label.., sep = "~~~~")),
               formula = y~x, parse = TRUE, label.x.npc = .5, color="blue")
```

### BONUS: Marginal Histograms
We can also add histograms to convey marginal distributions

```{r}
p1 <- ggplot(ex8_data, aes(CESD1, CESD2)) + 
  geom_point() + 
  geom_smooth(method=lm) +
  xlab("CESD at Time 1") + 
  ylab("CESD at Time 2") + 
  stat_poly_eq(aes(label =  paste(..eq.label.., ..adj.rr.label.., sep = "~~~~")),
               formula = y~x, parse = TRUE, label.x.npc = .5, color="blue") + 
  
  # Remove gridlines 
  theme_bw(base_size = 16) +
  theme(axis.text.x     = element_text(size = 12),
        axis.title.y    = element_text(vjust = +1.5),
        panel.grid.major  = element_blank(),
        panel.grid.minor  = element_blank(),
        legend.background = element_blank(),
        legend.key = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.line  = element_line(colour = "black"))

ggMarginal(
  p = p1,
  type = 'histogram',
  bins = 20,
  margins = 'both',
  size = 2,
  col = 'black',
  fill="grey"
)
```

